%_____________________________________________________________________________________________ 
% LATEX Template: Department of Comp/IT BTech Project Reports
% Abstract of Report
% Sun Mar 27 10:34:00 IST 2011
%_____________________________________________________________________________________________ 
\newpage
%\begin{abstract}
%\addcontentsline{toc}{chapter}{Abstract}	% This makes sure abstract is included in contents.
\begin{center}
\Large \textbf{Abstract}
\end{center}
	Chatbots are proving themselves quite useful now a days. Chatbots like
	Siri(iOS), Google Assistant(Android), Google Allo (Cross Platform),
	Cortana (Windows), Amazon Alexa and many more, are used daily by many
	people, in various parts of world. These chatbots help us accomplish
	many daily tasks like finding a location, booking a table at restaurant,
	calling someone, etc. 
	
	These chatbots are all open domain chatbots, i.e. they can be used for
	general purpose  tasks. But they are unable to perform specific tasks
	like answering questions which are specific to industry, education, or
	an organization. Such chatbots are called as closed domain chatbots.
	Many companies deploy such chatbots on their website to answer specific
	questions related to them. Most of the replies are pre-fed and if any
	new query comes to the chatbot, it either sends the query to the
	company’s concerned authority for a reply or straight away ignores the
	question.
	
	We will be focusing on how to build an open domain end-to-end
	conversation model for chatbots which shall test the users on their
	knowledge on any arbitrary topic they choose. The method used for open
	domain chatbots can be applied for closed domain chatbots as well if
	relevant data on that domain is available. The only problem faced by
	closed domain chatbots is that they lack datasets for development,
	whereas lots of data is available for open domain chatbots. 

%\end{abstract}

%_____________________________________________________________________________________________ 
