%_____________________________________________________________________________________________ 
% LATEX Template: Department of Comp/IT BTech Project Reports
% Sample Chapter
% Sun Mar 27 10:25:35 IST 2011
%
% Note: Itemization, enumeration and other things not shown. A sample figure is included.
%_____________________________________________________________________________________________ 

\chapter{Algorithm}
The complete work presented here can be divided into several parts right from taking in a topic as input, finding out relevant documents, tagging words as probable answer words, and eventually generating questions from it. 

\section{Topic Input and Data gathering}

Initially, the user shall enter his/her topic of interest into the software. The software shall then crawl the web and gather links to various web pages relevant to the topic given by the user. On getting the links, further the software shall scrape those links and parse the HTML pages to get the information content in those web pages. 
However, all the content received can be classified into three parts. The first part consists of markup language tasks and syntax, the second part shall contain data unrelated to the topic of interest, and the third shall be the data which is useful and relevant both to the topic of interest. The data classified into the first part, is removed by searching for markup language tasks in the obtained data. On finding such tags, the lines containing such tags shall be eliminated from the useful data text. For identifying data in the second part, the semantic meaning of the words and the web page from where the data has been input is taken into consideration. Thus eventually the system has data which can be used for generating questions on the users topic of interest. 

\section{Pre processing block}
The processing done at this stage can be broken down into 4 independent tasks. The output of each of these four tasks work as features for the question generation algorithm. The four tasks and their work can be summarized as follows - 

\begin{itemize}[align=left]
	\item [\textbf{1. Case of the word in context -}] 
This feature determines whether the first letter of the word is in lower or upper case. The output of this case thus determines whether the word is the starting word of the context. In quite a few cases, the starting word of the context.

	\item [\textbf{2. NER Tagging -}] 
The 7 set Stanford NER Tagging is used in the system. The NER Tagging helps in finding out a type of a noun the word is, like a place, a date or a person. As per the tag different Wh questions are created and hence the feature is of great significance in the problem.

	\item [\textbf{3. POS Tagging:}] 
	POS tags are important in generating patterns based on their frequency in the contexts. Frequently occuring series of consecutive POS tags that form answer words in the training sentences are most probable to be the best sources for generating questions in test contexts as well. 

	\item [\textbf{4. Answer Words:}]
	This feature is the most important of all the four features. This feature talks of whether the word in consideration is an answer word or not, in the question to be formed. Only those words that are answer words are given paramount importance in the question generating process. 

\end{itemize}

%Th is is a section. We can cite a reference like this: \cite{INTERNET} 	
						% Citation. See references.tex for the entry.
\section{Question Generation Algorithm}



\section{Output}
In the end, the system shall generate questions on either the topic of interest specified to the user or the text given as input to the system. The system can generate three types of questions. The first type is Fill in The Blank questions, where a factual or important word is left blank in a sentence from the input text. The second type is a one word answer, where an important sentence from the input text, is converted to a question and presented to the user. Finally, the system can also generate reading comprehension type of questions, wherein the input text on which questions are generated is made available to the user while he/she is answering the questions. 
